dyngen: a multi-modal simulator for spearheading new single-cell omics analyses

### 2020-02-06 manuscript.Rmd
change date to equal contribution

---
title: "dyngen: a multi-modal simulator for spearheading new single-cell omics analyses"
author:
- Robrecht Cannoodt*
- Wouter Saelens*
- Louise Deconinck
- Yvan Saeys
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    citation_package: biblatex
biblatexoptions: sorting=none
classoption:
- table
- 10pt
- a4paper
header-includes: |
  \usepackage{tcolorbox}
  \usepackage{colortbl}
  \usepackage{booktabs}
  \usepackage{tabularx}
  \usepackage{fontspec}
  \usepackage{pifont}
  \setmainfont [Path = fonts/,
    UprightFont = *-300,
    ItalicFont = *-300-Italic,
    BoldFont = *-700,
    BoldItalicFont = *-700-Italic
  ]{MuseoSans}
bibliography: library.bib
---

>>>>

---
title: "dyngen: a multi-modal simulator for spearheading new single-cell omics analyses"
author:
- Robrecht Cannoodt*
- Wouter Saelens*
- Louise Deconinck
- Yvan Saeys
date: "* Equal contribution"
output:
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    citation_package: biblatex
biblatexoptions: sorting=none
classoption:
- table
- 10pt
- a4paper
header-includes: |
  \usepackage{tcolorbox}
  \usepackage{colortbl}
  \usepackage{booktabs}
  \usepackage{tabularx}
  \usepackage{fontspec}
  \usepackage{pifont}
  \setmainfont [Path = fonts/,
    UprightFont = *-300,
    ItalicFont = *-300-Italic,
    BoldFont = *-700,
    BoldItalicFont = *-700-Italic
  ]{MuseoSans}
bibliography: library.bib
---
